### 2017-04-01 thesis/latex/thesis.tex
Thesis: minor additions.

The basic form is simple. Kinesin, myosin and dynein each have two foot domains which each alternatingly act as levers. One foot will bind to a surface and apply a force, levering the whole motor forward. This causes the other foot to bind and the cycle to repeat. This design is simple, but the ways each motor implement it are very different. Binding to the .........

>>>>

The basic form is simple. Kinesin, myosin and dynein each use two binding domains to attach to a surface. These binding domains are connected via a linker domain. Each motor protein is an engine which undergoes cycles, where each cycle moves the motor across a surface. In a cycle a binding domain will unbind from a surface, tense its foot to kick forward, rebind, then untense its foot to pull the whole motor forward. This pattern is repeated by both feet to generate motion \cite{kinesin-cycle} \cite{myosin-cycle}.\\
